Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-01 paper.tex
section refs and acknowledgment

\subsection{Overview}
\par Section 2 reviews some preliminary material.
Section 3 finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
Section 4 embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
We compute the Slodowy slice and end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par Section 5 discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
Section 6 solves the easier problem.
Section 7 finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
Section 8 applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
Section 9 discusses an interesting direction for future work.
Finally, section 10 proves some linear algebra lemmas that were used in the paper.

\subsection{Acknowledgment}
TODO.  UROP+ program and Haoshuo.
MIT (provided funding)?

@@

\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{prelim}
The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
In this section we use this to find that there is a unique principal \(\spl_2\)-triple in \(\gl_n\).
Write \(e = J_n\).
\begin{lemma}\label{simple_sl2_triple}
    There is exactly one way to choose \(h, f \in \gl_n\) so that \((e, h, f)\) is an \(\spl_2\)-triple.
\end{lemma}
\begin{proof}

>>>>

\subsection{Overview}
\par \cref{prelim} reviews some preliminary material.
\cref{principal_sl2} finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
\cref{find_sxn} embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
We compute the Slodowy slice and end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par \cref{p_comp_strat} discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
\cref{q_comp} solves the easier problem.
\cref{p_comp} finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
\cref{sxn_comps} applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
Finally, \cref{linalg} proves some linear algebra lemmas that were used in the paper.

\subsection{Acknowledgments}
Thank you to Haoshuo Fu for suggesting the fun project, guiding me through it, and helping me to learn many things, both by talking to me about them and by suggesting things to read.
Thank you also to the organizers of the MIT math department's UROP+ program, and to MIT for providing funding.

@@

\section{Principal \texorpdfstring{\(\spl_2\)}{sl\_2}-triple in \texorpdfstring{\(\gl_n\)}{gl\_n}}\label{principal_sl2}
The unique nilpotent regular element of \(\gl_n\) (up to similarity) is \(J_n\).
In this section we use this to find that there is a unique principal \(\spl_2\)-triple in \(\gl_n\).
Write \(e = J_n\).
\begin{lemma}\label{simple_sl2_triple}
    There is exactly one way to choose \(h, f \in \gl_n\) so that \((e, h, f)\) is an \(\spl_2\)-triple.
\end{lemma}
\begin{proof}
